When placing bets we trust the other(s) participant(s) or the institution
  holding the bet to pay us if we win.
In this work we propose a protocol on top of Bitcoin to place bets depending on
  real world events in a decentralized and trustless fashion.
Implementations of decentralized gambling on top of Bitcoin or other
  cryptocurrencies have been publicized for random events, trying to emulate
  some casino's game of chance, as the roulette or blackjack.
However a distributed solution for non random events is still an open problem.\\
\noindent
Our protocol uses a set ``oracles'' to bring the outcome of the bet's event into
  the blockchain.
When a certain threshold of the oracles have reported the same outcome for
  the event we unlock the winner's prize.
Protocol was designed to move the money to one of the players in the bet,
  oracles do not take control of the prize, they only decide between two
  possible outcomes.\\
\noindent
Economic incentives are placed to encourage good behavior of the participants,
  oracles get paid if and only if they provide the right answer, defined as the
  answer provided by the majority of them.
They are required to place a deposit to participate.
This allows the protocol to establish economic penalties if the oracle does not
  answer or does it wrong.\\
\noindent
Once the bet is placed, the prize is locked waiting for the oracles' answer,
  players lose the control of the money until the oracles decide the winner
  or a previously defined timeout is exceeded.
In which case each player gets half of the prize.\\
\noindent
Using Bitcoin scripting language the protocol guarantees fairness and correct
  execution with a dishonest minority of oracles and a dishonest peer, once the
  bet is placed.
Before the bet is placed a dishonest peer can cause limited economic damage to
  an honest player.
With an attack cost equal to the damage inflicted.
Dishonest oracles, before the bet is placed, can cause small economic damage to
  both players equally, the cost for this attack is a parameter set by the
  players.\\
\noindent
