\section{Conclusion}

Since the Bitcoin creation in 2008 more than a thousands of different
  cryptocurrencies have been created, most of them following its main design
  properties.
Bitcoin is known and often criticized because its slow evolution and resistance
  to changes.
This is accentuated for the overwhelming number of different and fast evolving
  currencies created.

A currency where rules does not change too much over time makes it a good store
  for value, and likely this property of bitcoin contributes to make it the
  most valuable cryptocurrency, as measured by market capitalization.
This is a desired feature for our algorithm, we don't want the value of the
  money put when the bet is placed to be too different of the one when the bet
  is resolved.

However this did not come for free, this slow change rate keeps bitcoin script
  language very limited.
When people talk about smart contract or scripting, Bitcoin is never the first
  currency to come to peoples' mind.
This limitation, the slow change rate and the biggest network made it our
  choice: the limitation poses the real challenge in the protocol presented.
The problem is trivial for currencies with more expressive scripting languages;
  the slow change rate helps to keep the currency value and the same rules from
  the start to the end of a bet; and finally to have the biggest network
  enforcing the protocol rules makes more difficult some known attacks, as
  Majority and Eclipse \cite{heilman2015attack}.
Other cost of using a limited scripting language is the amount of instructions
  and transactions required to express the protocol, this is traduced to a
  higher fee cost.



