\begin{enumerate}
  \item The first step is to compile a list of available oracles, we use as
      decentralized database for this list the blockchain. Everyone willing to
      be an oracle can send a transaction to register into the blockchain.
  \item The players negotiate some parameters, as the number of oracles to use
      and the threshold to decide the winner.
  \item In order to decide which oracles to use, the oracles need to pick a
      subset of the available oracles, they do this by running a distributed
      coin tossing protocol.
    With this, they can be sure the compiled list is a random subset of the
      full list. If the list is big enough, the chance of one user controlling
      the oracles gets smaller. As it would be too expensive to control almost
      all the oracles in the list.
\end{enumerate}


\begin{enumerate}
  \item The players send a transaction to the blockchain with the bet
      description, including the IDs of the oracles they want to decide the
      winner.
    We call this transaction ``Bet promise'',as the players commit to the bet by
      placing it. The wage is also on it.
    The other purpose of this transaction is to invite the oracles to
      participate in the bet, we make its ID public so they can identify itself
      and inscribe to participate as oracles.
  \item The oracles will see the transaction inviting them to participate in the
      bet, they will evaluate it and, if they are interested.
    They will reply with a transaction containing a reference to the ``Bet
      promise'' transacation and a small deposit as commitment that they will
      participate in the process.
  \item When the players see the answer from the expected number of oracles,
  	  they will send the ``Bet'' transaction with funds of the bet and the
  	  oracles' reward.
  	If not enough oracles reply to the call, a second invitation can be send to
  	  a different set of oracles to fill the available spots.
  \item As soon as the bet event takes place, oracles are able to collect its
  	  payment from the Bet transaction. This payment gets available by making
  	  public, -voting- by the winner.
  	After the threshold number of oracles collect its payment, the winner player
  	  is able to collect its prize, its private key and the oracle votes are
  	  required to get it.
  \item After a second timeout, players can take the deposit from the oracles
  	  that did not participate in the bet resolution.
\end{enumerate}

The payment of the oracle's is not the only cost of this protocol.
There is a not insignificant number of transactions in the protocol, as there
  is a fee by each transaction in the Blockchain, this makes the protocol more
  expensive.
This is a problem for small bets, the presented protocols is prohibitively
  expensive for bet of just a few dollars. At least with the current fee costs
  of bitcoin.

If we step out a little bit, the proposed protocol uses paid oracles to get a
  binary answer about an event outside the blockchain. This is not useful only
  for betting on that outcome. The oracles are \footnote{\colorbox{red}{
  is this the word?}} insensitive to the use given to their answer, they get
  paid anyway. Further applications of the protocol can be generalized from our
  proposal.
Resolution of contractual disputes is an interesting topic, where parties agree
  to use arbitrator(s) to decide a missunderstanding.
In this case oracles takes part in the protocol more like judge than a oracle.
